### 2016-05-30 text/Chapter04.tex
Edits and tweaks (Chapter 8 and 9 mostly)

Recall the lambda abstraction rules for the implicit parameters coeffect system (annotating
contexts with sets of required parameters) and the dataflow system (annotating contexts with the
number of past required values):
%
\begin{equation*}
\tyrule{param}
  {\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{r} \cup \cclrd{s}} \vdash e : \tau_2}
  {\coctx{\Gamma}{\cclrd{r}} \vdash \lambda x.e : \tau_1 \xrightarrow{\cclrd{s}} \tau_2 }
\;
\tyrule{df1}
  {\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{n}} \vdash e : \tau_2}
  {\coctx{\Gamma}{\cclrd{n}} \vdash \lambda x.e : \tau_1 \xrightarrow{\cclrd{n}} \tau_2 }
\end{equation*}
%
In order to capture both systems using a single calculus, we need a way of rewriting the
(\emph{df1}) rule such that the annotation in the assumption is in the form $\cclrd{n \disc m}$
for some operation $\cclrd{\disc}$. For the dataflow system, this can be achieved by using
the $\cclrd{\emph{min}}$ function:
%
\begin{equation*}
\tyrule{df2}
  {\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{\textnormal{min}(n, m)}} \vdash e : \tau_2}
  {\coctx{\Gamma}{\cclrd{n}} \vdash \lambda x.e : \tau_1 \xrightarrow{\cclrd{m}} \tau_2 }
\end{equation*}
%
The rule (\emph{df1}) is admissible in a system that includes the (\emph{df2}) rule. That is,
a typing derivation using (\emph{df1}) is also valid when using (\emph{df2}). Furthermore,
if we include sub-typing rule (on annotations of functions) and subcoeffecting rule (on
annotations of contexts), then the reverse is also true -- because
$\cclrd{\textit{min}(n, m)} \leq \cclrd{m}$ and $\cclrd{\textit{min}(n, m)} \leq \cclrd{n}$.
In other words (\emph{df2}) permits an implicit subcoeffecting (and sub-typing) that is not
possible when using the (\emph{df1}) rule, but it has a structure that can be unified
with (\emph{param}).

>>>>

Recall the lambda abstraction rules for the implicit parameters coeffect system (annotating
contexts with sets of required parameters) and the dataflow system (annotating contexts with the
number of past required values):
%
\begin{equation*}
\tyrule{param}
  {\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{r} \cup \cclrd{s}} \vdash e : \tau_2}
  {\coctx{\Gamma}{\cclrd{r}} \vdash \lambda x.e : \tau_1 \xrightarrow{\cclrd{s}} \tau_2 }
\;
\tyrule{df1}
  {\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{n}} \vdash e : \tau_2}
  {\coctx{\Gamma}{\cclrd{n}} \vdash \lambda x.e : \tau_1 \xrightarrow{\cclrd{n}} \tau_2 }
\end{equation*}
%
In order to capture both systems using a single calculus, we need a way of rewriting the
(\emph{df1}) rule such that the annotation in the assumption is in the form $\cclrd{n \circ m}$
for some operation $\cclrd{\circ}$. For the dataflow system, this can be achieved by using
the $\cclrd{\emph{min}}$ function:
%
\begin{equation*}
\tyrule{df2}
  {\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{\textnormal{min}(n, m)}} \vdash e : \tau_2}
  {\coctx{\Gamma}{\cclrd{n}} \vdash \lambda x.e : \tau_1 \xrightarrow{\cclrd{m}} \tau_2 }
\end{equation*}
%
The rule (\emph{df1}) is admissible in a system that includes the (\emph{df2}) rule. That is,
a typing derivation using (\emph{df1}) is also valid when using (\emph{df2}). Furthermore,
if we include sub-typing rule (on annotations of functions) and subcoeffecting rule (on
annotations of contexts), then the reverse is also true -- because
$\cclrd{\textit{min}(n, m)} \leq \cclrd{m}$ and $\cclrd{\textit{min}(n, m)} \leq \cclrd{n}$.
In other words (\emph{df2}) permits an implicit subcoeffecting (and sub-typing) that is not
possible when using the (\emph{df1}) rule, but it has a structure that can be unified
with (\emph{param}).

### 2016-05-30 text/Chapter07.tex
Edits and tweaks (Chapter 8 and 9 mostly)

This illustrates the difference between the two -- the flat system keeps only one annotation
for the whole body (which requires 1 past value). In lambda abstraction (or function declaration
written using \kvd{let}), this requirement is duplicated. The structural system keeps information
per-variable and so the resulting type reflects the fact that only the variable \idnet{y} appears
inside \kvd{prev}.

@@

\paragraph{Targetting JavaScript.} In order to make the implementation accessible to a broad
audience, it can be executed in a web browser. This is achieved by automatically translating the
implementation from F\# to JavaScript. We use an F\# library called FunScript \cite{other-funscript}
(which is a more recent incarnation of the idea developed by the author \cite{app-fsharp-webtools}).
We choose F\#, but similar tools exist for other functional languages such as OCaml \cite{other-js-ocaml}.
It is worth noting that FunScript is implemented as a \emph{library} rather than as a compiler
extension. This is done using the meta-programming capabilities of F\# \cite{app-fsharp-metaprog}.

>>>>

This illustrates the difference between the two -- the flat system keeps only one annotation
for the whole body (which requires 1 past value). In lambda abstraction (or function declaration
written using \kvd{let}), this requirement is duplicated. The structural system keeps information
per-variable and so the resulting type reflects the fact that only the variable \ident{y} appears
inside \kvd{prev}.

@@

\paragraph{Targetting JavaScript.} In order to make the implementation accessible to a broad
audience, it can be executed in a web browser. This is achieved by automatically translating the
implementation from F\# to JavaScript. We use an F\# library called FunScript \cite{other-funscript}
(which is a more recent incarnation of the idea developed by the author \cite{app-fsharp-webtools}).
We choose F\#, but similar tools exist for other functional languages such as OCaml \cite{app-ocaml-js}.
It is worth noting that FunScript is implemented as a \emph{library} rather than as a compiler
extension. This is done using the meta-programming capabilities of F\# \cite{app-fsharp-metaprog}.
